% =====================================================
% ===================== ENGLISH =======================
% =====================================================

\cvheader{Juan Diego Figari}{Buenos Aires, Argentina}{juancito.diego@gmail.com}{https://github.com/Yarthax23}

\section*{Summary}
Intermediate Computer Science student at UBA with a systems-oriented focus.
Experience designing and implementing event-driven servers in C, REST APIs in Go,
and functional programs in Haskell and Prolog. Strong emphasis on explicit protocol
design, state ownership, and incremental, correctness-first development on Linux.

\section*{Skills}
\begin{itemize}
  \item \textbf{Languages:} C, Go, Python, Haskell, Prolog, Java (light), JavaScript, HTML/CSS
  \item \textbf{Systems / Concepts:} UNIX domain sockets, TCP fundamentals, \texttt{select()}, event-driven I/O, protocol framing, client-server architectures, explicit state ownership
  \item \textbf{Tools / Misc:} Linux, Bash, Git, Valgrind, GDB, QEMU, PostgreSQL, CURL, basic scripting and automation, security wargames (OverTheWire)
  \item \textbf{Areas:} Algorithms, data structures, systems programming, OOP, functional \& logic programming
\end{itemize}

\section*{Projects}
\noindent \textbf{Event-Driven Chat Server in C} \hfill \textit{2025} \\
\href{https://github.com/Yarthax23/unix-chat-server}{GitHub Repository}
\begin{itemize}
  \item Single-process, single-threaded, multi-client chat server using UNIX domain sockets (\texttt{AF\_UNIX}, \texttt{SOCK\_STREAM}) with \texttt{select()}.
  \item Layered protocol: framing, grammar, execution; explicit state ownership and deterministic transitions.
  \item Incremental, auditable design prioritizing correctness and debuggability.
\end{itemize}

\noindent \textbf{REST API To-Do Server in Go} \hfill \textit{2025} \\
\href{https://github.com/Yarthax23/go-todo-api}{GitHub Repository}
\begin{itemize}
  \item REST endpoints with basic authentication, PostgreSQL integration, and \texttt{curl}-based testing.
  \item Early Go project focused on learning the language, standard library usage, and backend API structure.
\end{itemize}

\noindent \textbf{Functional \& Logic Programming Work} \hfill \textit{2025} \\
\href{https://github.com/juop12/Exactas-PLP-cNil}{GitHub Repository}
\begin{itemize}
  \item Haskell \& Prolog exercises: recursive structures, type-safe functional patterns, logic-based problem solving.
  \item Introduced to commit conventions and basic TDD practices.
\end{itemize}

\section*{Education}
\textbf{Bachelor in Computer Science} — University of Buenos Aires, in progress (53\% completed)

\noindent \textbf{Bilingual High School (Science \& Computer Focus)} — Liceo Franco Argentino Jean Mermoz

\section*{Languages}
\begin{itemize}
  \item Spanish: Native
  \item English: Advanced
  \item French: Advanced
\end{itemize}

\section*{Experience}
\textbf{McDonald's - Arcos Dorados S.A.} \hfill 2023-2024
\begin{itemize}
  \item Customer service, cash handling, end-of-day closing; recognized as standout performer.
\end{itemize}

\noindent \textbf{Piano Instructor (freelance)} \hfill 2021-2025
\begin{itemize}
  \item Private lessons and autonomous student management.
\end{itemize}